---
title: "Assignment - 2"
author: "Vamshee Deepak Goud Katta"
date: "11/17/2021"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Creating variables.

```{r}

set.seed(123)
X=runif(100)*10
Y=X*4+3.45
Y=rnorm(100)*0.29*Y+Y

```

### a) Plotting Y against X.

```{r}

plot(X,Y)

# Based on the data in graph, we can fit a linear model to explain Y based on X.

```

### b) Constructing a simple linear model of Y based on X.

```{r}

Model = lm(Y~X)
summary(Model)

Model$coefficients
 
```

The following equation explains Y based on X:

Y = (3.945235*X) + 3.274645

The accuracy of the model is 0.7038.

### c) Relation of Coefficient of Determination to the correlation coefficient of X and Y.

 A. R2 is the squared value of the coorelation cofficient between x and y where as, regression is based on one variable.

```{r}

cor(X,Y)^2

# From the above result, we can notice that it's the same value as R-squared '0.7038'.

```

## 2. Using ‘mtcars’ dataset.

```{r}

head(mtcars) 

```

### a) Constructing simple linear models using mtcars data to determine better estimator of Horse Power (hp) or cars.

```{r}

James <- lm(mtcars$hp~mtcars$wt, data = mtcars)
summary(James)

Chris <- lm(mtcars$hp~mtcars$mpg, data = mtcars)
summary(Chris)

```

As per the linear models constructed using mtcars dataset, Chris is right to think that fuel consumption expressed in miles per gallon (mpg) is a better estimator of a car's horse power (hp).

Accuracy of Chris' model is 0.6024 which is higher compared to James' model which is only 0.4339

 

### b) Building linear model that uses the number of cylinders (cyl) and the mile per gallon (mpg) values of a car to predict the car HorsePower (hp).

```{r}

Model2 <- lm(mtcars$hp~mtcars$mpg+mtcars$cyl, data = mtcars)
summary(Model2)

Model2$coefficients

HP <- (Model2$coefficients[2]*22) + (Model2$coefficients[3]*4) + Model2$coefficients[1]
HP
 
```
The estimated Horse Power of a car with 4 cylinders giving 22 miles per gallon (mpg) is 88.93618

## 3.Boston Housing

### a) Building linear model to estimate the median value of owner-occupied homes (medv).

```{r}

library(mlbench)
data(BostonHousing)
 
Model3 <- lm(formula = BostonHousing$medv ~ BostonHousing$crim + BostonHousing$zn + BostonHousing$ptratio + BostonHousing$chas, data = BostonHousing)
summary(Model3)
 
```

The accuracy of this linear model is very low as the value of R2 is very low (0.3599).

### b) Using the estimated coefficient.

### I. Determining more expensive of the identical houses based on relation to the Chas River.

```{r}

summary(Model3)

```

Based on the above summary, the estimate of the  variation of identical houses in expense is $4.58k as the change in value of house that bounds chas river and that doesn't is 1.

### II. Determining the more expensive of the identical houses along with the value based on pupil-teacher ratio in the neighborhoods.

```{r}

# Estimate of the variation of identical houses in expense can be found by multiplying the estimate coefficient with the difference in pupil-teacher ratio among them.

X <- -1.49367*(15-18)
X

```

### c) Determining statistically important variables.

```{r}

summary(Model3)

```

Based on the above result, P-value for the model is <0.05. Hence, none of the variables are statistically important.

### d) Using the anova analysis to determine the order of importance of variables.

```{r}

anova(Model3)
 
```

According to the analysis, the order of importance of the variables can be interpreted as

crim > ptratio > zn > chas
