---
title: "Assignment_1"
author: "Vamshee Deepak Goud Katta"
date: "10/20/2021"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Reading data file

```{r}
library(dplyr)
library(readr)
Retail <- read.csv("Online_Retail.csv")

```

# 1. Breakdown of transactions by country

```{r}

Retail1  <- as.data.frame(table(Retail$Country))
Percentage <- Retail1$Freq/NROW(Retail) * 100
Retail1 <- cbind(Retail1, Percentage) 
names(Retail1) <- c("Country","Total Transactions","Percentage")
Retail1[Retail1$Percentage > 1,]

```

# 2. Creating variable 'TransactionValue'

```{r}

TransactionValue <- Retail$Quantity*Retail$UnitPrice
Retail2 <- cbind(Retail, TransactionValue)
head(Retail2)

```

# 3. Breakdown of transaction values by countries exceeding 130000

```{r}

Retail3 <- Retail2%>%group_by(Country)%>%
  summarise(Total=sum(TransactionValue))
Retail3[Retail3$Total>130000,]

```
# 4. Golden Questions

## Converting ‘InvoiceDate’ into a POSIXlt object
```{r}

Retail4 <- Retail
Temp=strptime(Retail4$InvoiceDate,format='%m/%d/%Y %H:%M',tz='GMT')
Retail4$New_InvoiceDate <- as.Date(Temp)
Retail4$New_InvoiceDate[20000]- Retail4$New_InvoiceDate[10]
Retail4$Invoice_Day = weekdays(Retail4$New_InvoiceDate)
Retail4$Invoice_Hour = as.numeric(format(Temp, "%H"))
Retail4$Invoice_Month = as.numeric(format(Temp, "%m"))

```

## a) Percentage of transactions (by numbers) by days of the week

```{r}

Retail4%>%group_by(Invoice_Day)%>%
  summarise(count=n())%>%
  mutate(Percentage=count/nrow(Retail4)* 100)

```

## b) Percentage of transactions (by transaction volume) by days of the week

```{r}

Retail4%>%group_by(Invoice_Day)%>%
  summarise(Total=sum(TransactionValue))%>%
  mutate(Percentage=Total/sum(Total)*100)

```

## c) Percentage of transactions (by transaction volume) by month of the year

```{r}

Retail4%>%group_by(Invoice_Month)%>%
  summarise(Total=sum(TransactionValue))%>%
  mutate(Percentage=Total/sum(Total)*100)

```

## d) Date with the highest number of transactions from Australia

```{r}

Retail4%>%
filter(Country=="Australia")%>%
group_by(New_InvoiceDate)%>%
tally(sort = TRUE)%>%  
filter(n==max(n))

```

# 5. Histogram of transaction values from Germany

```{r}

Retail4%>%
group_by(Country)%>%
filter(Country=="Germany")%>%
group_by(Invoice_Month)%>%
summarise(Total = sum(TransactionValue))-> Germany
hist(Germany$Total, main = "Transaction Values", xlab = "Total Value", ylab = "Months")

```

# 6. Customer with highest number of transactions

```{r}

Retail%>%
group_by(CustomerID)%>%
tally(sort = TRUE)%>%
filter(!is.na(CustomerID))%>%  
filter(n==max(n))

```

# Most Valuable Customer

```{r}

Retail2%>%
group_by(CustomerID)%>%
summarise(Total=sum(TransactionValue))%>%
filter(!is.na(CustomerID))%>%  
filter(Total == max(Total))

```

# 7. Percentage of missing values

```{r}

colMeans(is.na(Retail2) *100)

```

# 8. Number of transactions with missing CustomerID records by countries

```{r}

Retail2%>%
  group_by(Country)%>%
  summarise(Total=nrow(Retail2[is.na(Retail2$CustomerID),]))

```

# 10. Return rate for the French customers

```{r}

Retail10c <- Retail2%>%
  filter(Country=="France", Quantity<0)%>%
  count
Retail10t <- Retail2%>%
  filter(Country=="France")%>%
  count
Retail10 <- (Retail10c$n / Retail10t$n) * 100
Retail10

```

# 11. Product with highest revenue

```{r}

Retail2%>%
  group_by(Description)%>%
  summarise(Total=sum(TransactionValue))%>%
  arrange(desc(Total)) %>%
  head(100)

```
## Postage is not an actual product. Hence the product with highest revenue is 'REGENCY CAKESTAND 3 TIER'

# 12. Unique customers in the dataset

```{r}

Retail12 <- unique(Retail2$CustomerID, fromLast = FALSE,nmax = NA)
length(Retail12)
  
```

# 9. Average number of days between consecutive shopping

